Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-10 podc16/paper2.tex
Added comments on the basic model and commutativity.

We consider a set of processes $P$ subject to crash-stop faults and communicating by message-passing in an asynchronous network.
We also consider a deterministic state-machine $M$ whose set of commands is $C$. We say that two commands $c_a$, $c_b$ \textit{commute} if executing $c_a$ before $c_b$ has the same effect as executing $c_b$ before $c_a$. We also consider a symmetric relation $R \subseteq C\times C$, called \textit{dependency relation}, such that: for any command $c$, $\left( c,c \right)\notin R$;  if $\left( c_a,c_b \right)\notin R$ $c_a$, $c_b$ \textit{commute}. then $\aseq{s_1,c_1,\cdots,s_i,c_a,s_{i+1},c_b,s_{i+2}\cdots,s_n}$ is an execution of the state-machine $M$ if and only if
%$\aseq{s_1,c_1,\cdots,s_i,c_b,s_{i+1},c_a,\cdots,s_n}$.
%$\aseq{s_1,c_1,\cdots,s_i,c_b,s_{i+2},c_a,s_{i+1},\cdots,s_n}$

>>>>

We consider a set of processes $P$ subject to crash-stop faults and communicating by message-passing in an asynchronous network.
We also consider a deterministic state-machine $M$ whose set of commands is $C$. 
We say that two commands $c_a$, $c_b$ \textit{commute} if executing $c_a$ before $c_b$ has the same effect on the state machine as executing $c_b$ before $c_a$. We assume that a command does not commute with itself.
We also consider a symmetric relation $R \subseteq C\times C$, called \textit{dependency relation}, such that: for any command $c$, $\left( c,c \right)\notin R$, and if $\left( c_a,c_b \right)\notin R$ then $c_a$ and $c_b$ commute.

\todo{Why do we need $R$ if we already define what commute and non-commutative means?}

\todo{About the uniqueness of commands: why not leave that our of our scope?}

\todo{Why not base everything on C-Structs? We can say that two commands commute when $\sigma\bullet c_1\bullet c_2 =  \sigma\bullet c_2\bullet c_1 $ for every cstruct $\sigma$.}
